%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{xcolor}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Japnit}{\color{red} Singh} { \urlstyle{same}\href{http://japnit.net}{japnit.net} | 
\href{mailto:singj36@mcmaster.ca}{singj36@mcmaster.ca} | +91-9811754575 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{{\color{red}Education}}
\smallskip
\subsection{McMaster University}
\descript{B.Sc in Computer Science}
\location{May 2023 | Hamilton, ON}
Major GPA: 3.9 / 4.0
\sectionsep

\subsection{Birla Vidya Niketan}
\descript{High School}
\location{May 2019 | New Delhi, IN}
\location{ Aggregate : 95.5 \%
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{red}Links} 
\smallskip
Github:// \href{https://github.com/japnits}{\bf japnits} \\
LinkedIn://  \href{https://www.linkedin.com/in/japnit-singh}{\bf japnit-singh} \\
Facebook://  \href{https://www.facebook.com/japnit.singh.583}{\bf Japnit Singh}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{red}{Course}work  }

\smallskip
\subsection{Undergraduate}
Data Representation, Computer Architecture, Analyzing and Problem Solving \\
Discrete Math\\
Unix Tools and Scripting \\
Data Structures \& Algorithms\\
Functional Programming(Haskell) \\
Objective Oriented Programming\\


\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{red} Skills }
\smallskip
\subsection{Programming}
\smallskip
\location{Expertise In:}
\smallskip
\textbullet{} Java   \\ \textbullet{} C++ \\  \textbullet{} Python \\ \textbullet{} Javascript \\
\textbullet{} Matlab \\ \textbullet{} Shell \\ \textbullet{} \LaTeX\ \\ 
\textbullet{} Django \\ 
\textbullet{} Node.js \\ 
\textbullet{} React.js \\ 
\textbullet{} HTML \\ 
\textbullet{} CSS \\
\textbullet{} PHP\\
\textbullet{} MySQL \\ 
\textbullet{} MongoDB \\ 
\textbullet{} Assembly \\


\sectionsep
\section{\color{red} Hackathons }
\textbullet{} Starter Hacks, UWaterloo \\
\textbullet{} Hack Western, WesternU \\
\textbullet{} Delta Hacks, McMasterU \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{red}Experience}
\smallskip
\runsubsection{Giden}
\descript{| Web Developer Intern }
\smallskip
\location{Sept 2020 - Present | Toronto, ON}

\sectionsep


\runsubsection{Contack \& Team Leader }
\descript{| Software Engineering Intern }
\smallskip
\location{Apr 2020 – Aug 2020 | Boston, MA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item SAAS platform development to raise funding for the startup.
\item Designed an efficient and cost-effective AWS solution for the application. 
\item Existing website redesign using the desired technology stack to increase web traffic by 50\%
\item Engaged and co-ordinated regularly with different channels practising agile methodology of development.
\end{tightemize}
\sectionsep


\runsubsection{Kobal Sales \& Marketing }
\descript{| Shopify Web Stylist }
\location{Oct 2019 – Mar 2020 | Mississauga, ON}
\begin{tightemize}
\smallskip
\item Designed and customized the Shopify website of the KSM toys store using CSS .\\
\item Advertisement Campaign Manager for the business increasing web traffic and conversions per dollar spent by 70\%.\\
\end{tightemize}
\sectionsep


\runsubsection{Tann Trim}
\descript{| Web Developer Intern }
\location{Jun 2019 – Aug 2019 | New Delhi, IN}
\begin{tightemize}
\smallskip
\item Worked in a team, developing an ecommerce website for a Leather Goods Startup.

\item Built a Web Scraper to scrape e-commerce websites, modifying, and analyzing data hence increasing sales by influencing the business model.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{red}Projects}
\runsubsection{\href{https://github.com/JapnitS/CS1XA3/tree/master/Project03}{Social Media Clone} }

\location{Web Development}
\begin{tightemize}
\item App capable of authenticating user, sending/receiving friend requests, post/like status, change profile information.
\item Developed a web app using HTML, CSS, BootStrap, JS and Django, MySQL.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://github.com/JapnitS/CS1XA3/tree/master/}{Weather Application}}

\location {Web Development}
\begin{tightemize}
\item Developed a weather application which fetches real time weather data using Google Maps API.
\item Used Node.js Postgres, and Geo Weather API’s to establish the backend of the application	
\end{tightemize}
\sectionsep
\runsubsection{\href{https://github.com/JapnitS/CS1XA3/tree/master/Project01}{Bash File Manager}}

\location {Unix, Bash}
\begin{tightemize}
\item  Wrote a script that manages files based on user inputted parameters.
\item Capable of changing file permissions through basic English commands
rather than inputting code.
\item Finds the number of aux-verbs, vowels from a selected file.

\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\color{red} Awards} 
\begin{tabular}{rll}
2020         & Cum. GPA (3.9/4.0)       & Deans's Honor List\\
2019	     & Scholarship(>95 \% agg)  & McMaster President Entrance Award\\
\end{tabular}
\sectionsep



\end{minipage} 
\end{document}  \documentclass[]{article}
